A new method to estimate dark matter halo concentrations

### 2015-01-26 paper/article.tex
abstract, mergerd figure 1 and figure 4

\begin{abstract}
asd
\end{abstract}
\begin{keywords}
methods: numerical, galaxies: haloes, cosmology: theory, dark
matter
\end{keywords}

@@

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{nfw_normalized.pdf}
\end{center}
\caption{Dimensionless mass profiles as a function of the
  dimensionless radius for different concentration values.
    \label{fig:profiles}}
\end{figure}

@@

In Figure \ref{fig:velocity} we show the circular velocity profile for the same
concentrations as in Figure \ref{fig:profiles}.

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{vel_normalized.pdf}
\end{center}
\caption{Dimensionless velocity profiles as a function of the
  dimensionless radius for different concentration values.
    \label{fig:velocity}}
\end{figure}

@@

\begin{equation}
\avg{|D|}=\frac{1}{\left|{\cal{H}}_N\right|}\sum_{{\cal{H}}_N} |D|,
\end{equation}

where ${\cal{H}}_N$ corresponds to the set of haloes with $N$
particles, $D$ follows the definition in Eq. (\ref{eq:D}) and
$\left|{\cal{H}}_n\right|$ is the number of haloes in ${\cal{H}}_n$.

@@

\subsection{Tests on N-body data}
\label{sec:data}
\begin{figure}
  \begin{center}
    \includegraphics[width=0.48\textwidth]{mass-velocity.pdf}
  \end{center}
  \caption{Comparison between the obtained concentrations by our method and the velocity method
  \label{fig:mdv}}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=0.48\textwidth]{mass-density.pdf}
  \end{center}
  \caption{Comparison between the obtained concentrations by our method and the density method
  \label{fig:mdv}}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=0.48\textwidth]{density-velocity.pdf}
  \end{center}
  \caption{Comparison between the obtained concentrations by the density method and the velocity method
  \label{fig:mdv}}
\end{figure}

>>>>

\begin{abstract}

We present a new method to estimate the concentration of dark matter
halos in N-body simulations. Our method is based on a fit to the
integrated mass density as a function of halo radius. 
The advantage of this method is that the full particle information
without any binning. 
We test our method both on mock and N-body halos to compare it against
two popular methods to find concentrations: radial particle binning to
estimate the density and the maximum radial velocity. 
Tests on the mock halos show that the accuracy of our method to
recover input concentrations can achieve $0.1\%$ whil for the maximum
radial velocity and density methods it is on the order of $0.5\%$ and
$40\%$ respectively. 
We also measure the mass-concentration relationship on the N-body data with
the three methods. With respect to the other two approaches our method
produces a flatter relationship, while its normalization falls below
the maximum velocity method and above the density method.

\end{abstract}
\begin{keywords}
methods: numerical, galaxies: haloes, cosmology: theory, dark
matter
\end{keywords}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.48\textwidth]{nfw_normalized.pdf}
  \includegraphics[width=0.48\textwidth]{vel_normalized.pdf}
\end{center}
\caption{Dimensionless mass (left) and velocity (right) profiles as a
  function of the dimensionless radius for different concentration
  values. \label{fig:profiles}}
\end{figure*}

@@

@@

In the right panel of Figure \ref{fig:profiles} we show the circular
velocity profile for the same concentrations as in the left panel of
Figure \ref{fig:profiles}.

@@

@@

\begin{equation}
\avg{|D|}=\frac{1}{\left|{\cal{H}}_N\right|}\sum_{{\cal{H}}_N} |D|,
\end{equation}
%
where ${\cal{H}}_N$ corresponds to the set of haloes with $N$
particles, $D$ follows the definition in Eq. (\ref{eq:D}) and
$\left|{\cal{H}}_n\right|$ is the number of haloes in ${\cal{H}}_n$.

@@

\subsection{Tests on N-body data}
\label{sec:data}
\begin{figure*}
  \begin{center}
    \includegraphics[width=0.48\textwidth]{mass-velocity.pdf}
    \includegraphics[width=0.48\textwidth]{mass-density.pdf}
  \end{center}
  \caption{Comparison between the concentrations measured by our
    method and the maximum velocity (left) and density (right)
    methods. The line indicates the equal value between the two
    techniques.
  \label{fig:mdv}}
\end{figure*}
